---
title: "p039_normative_postproc"
author: "DVP"
date: "2022.12.12"
output: html_document
---

# merge normative data. extract QR info, compare with different calibration options
# setup
## dirs and libraries
```{r setusp, }
library(psych)
library(multcomp)
library(here)
library(rio)
library(lmerTest)
library(patchwork)
library(viridis)
library(ggseg)
library(kableExtra)
library(emmeans)
library(broom)
library(tidyverse)
options(bitmapType = "cairo")
source(here("scripts/reliability_scripts/helper_reliability_postproc_v2.r"))

# set dirs
outdir=here('data_reliability_long/df_mri/all')
analysis = 'single_rois'
outreliability = file.path(outdir, "empirical")
outreliability.comp = file.path(outdir, "computational")
try(dir.create(outreliability))
try(dir.create(outreliability.comp))
try(dir.create(file.path(outreliability.comp, analysis)))
theme_set(theme_minimal())
```

## files and features
```{r files and features}
df.harmonize = import(file.path(outdir, 'harmonize_variables.xlsx'))
df.harmonize = df.harmonize %>% dplyr::select(normative_modelling, modality)
names(df.harmonize)[1] = "feature"

df.parameters = import(here('data_reliability_long/df_mri/all/computational_parameters.xlsx')) %>% 
  mutate(sele_mean_mean = as.numeric(sele_mean_mean),
         sele_mean_sd = as.numeric(sele_mean_sd), 
         slee_change_var = as.numeric(slee_change_var),
         `Sele:mean_change7` = as.numeric(`Sele:mean_change7`))
df.parameters = left_join(df.parameters, df.harmonize)

rm_vars_error = retrieve_rm_vars_error()
rm_globalvars_error = retrieve_rm_globalVars_error()
```

## define models
```{r open models}
# define model1 
modelname = "model1"
df.model = 
  df.parameters %>% 
  dplyr::select(feature, 
                modality, 
                mean_70y, 
                sd1, 
                ch5, 
                sdDelta, 
                pct.err.mean_all)

 df.model = rename_model(df.model)
 write.csv(df.model,
            file = file.path(outreliability.comp, 
                             paste(modelname, 
                                   "csv",
                                   sep = ".")))
 
# define model2
modelname="model2"
df.model = 
  df.parameters %>% 
  dplyr::select(feature, 
                modality, 
                mean_70y, 
                sd1, 
                ch5,
                madDelta_cross, 
                pct.err.mean_all_cross)

 df.model = rename_model(df.model)
 write.csv(df.model,
            file = file.path(outreliability.comp, 
                             paste(modelname, 
                                   "csv",
                                   sep = ".")))

 # merge models
model1 = import(file.path(outreliability.comp, "model1.csv")) %>% 
  mutate(model = "model1")
model2 = import(file.path(outreliability.comp, "model2.csv")) %>% 
  mutate(model = "model2")

model = rbind(model1, model2)
model = 
  model %>%
  rowwise() %>% 
  mutate(f = gsub(paste0("_",modality), "", feature))
```

# Reliability - Based on Formula
## icc - formula
```{r}
df.formula.icc = expand.grid(feature = unique(model$feature),
            model = unique(model$model), 
            t = seq(3,9,by = 2), 
            total_time = seq(2,12, by =2)) %>% 
  left_join(model, .) %>% 
  mutate(ws = meanE^2*((total_time^2*t*(t+1))/ (12*(t-1)))^-1, 
         bs = seD^2, 
         icc = bs /(ws + bs))
save(df.formula.icc, file = file.path(outreliability.comp, "icc.formula.rda"))

# ws within-subject variability
  # for equispaced timepoints
   #e² / (t²*n*(n-1)/12*(n-1)
   # e = error
   # t = time
   # n = number of timepoints

  # bs = var(bs) = sd² = seD²


#ICC(2,1) = bs² / bs² + ws 
# in the context of long trajectories 

df.formula.icc = 
  df.formula.icc %>%
  mutate(sd_error = sqrt(ws), 
         mean1 = meanD + seD, 
         mean2 = meanD - seD)

df.formula.icc = compute_overlap(df.formula.icc)
df.formula.icc =df.formula.icc %>% ungroup()
save(df.formula.icc, file = file.path(outreliability.comp, "icc.formula.rda"))
```

## icc - formula - globalvars
```{r globalvars}
modelname = "model1_global"
df.model1 = 
  df.parameters %>% 
   dplyr::select(feature, 
                modality, 
                mean_70y, 
                sd1, 
                ch5, 
                sdDelta, 
                pct.err.mean_all)

 df.model1 = rename_model(df.model1, globalVars = T)
 write.csv(df.model1,
            file = file.path(outreliability.comp, 
                             paste(modelname, 
                                   "csv",
                                   sep = ".")))
 
# modelname="model2_global"
# df.model2 = 
#   df.parameters %>% 
#   dplyr::select(feature, 
#                 modality, 
#                 mean_70y, 
#                 sd1, 
#                 ch5,
#                 madDelta, 
#                 pct.err.median_all)
# 
# df.model2 = rename_model(df.model2, globalVars = T)
#  write.csv(df.model2,
#             file = file.path(outreliability.comp, 
#                              paste(modelname, 
#                                    "csv",
#                                    sep = ".")))

model1 = import(file.path(outreliability.comp, "model1_global.csv")) %>% 
  mutate(model = "model1")
# model2 = import(file.path(outreliability.comp, "model2_global.csv")) %>% 
#   mutate(model = "model2")

#model = rbind(model1, model2)
model = model1
model = 
  model %>% 
  rowwise() %>% 
  mutate(modality = if_else(feature == "MeanThickness", "thickness",
                            if_else(feature == "CorticalArea", "area",
                                    if_else(feature == "SubCorticalVolume", "svolume", "volume"))),
         f = gsub(paste0("_",modality), "", feature))

df.formula.icc = expand.grid(feature = unique(model$feature),
            model = unique(model$model), 
            t = seq(3,9,by = 2), 
            total_time = seq(2,12, by =2)) %>% 
  left_join(model, .) %>% 
  mutate(ws = meanE^2*((total_time^2*t*(t+1))/ (12*(t-1)))^-1, 
         bs = seD^2, 
         icc = bs /(ws + bs))
save(df.formula.icc, file = file.path(outreliability.comp, "icc.formula.global.rda"))


df.formula.icc = 
  df.formula.icc %>%
  mutate(sd_error = sqrt(ws), 
         mean1 = meanD + seD, 
         mean2 = meanD - seD)

df.formula.icc = compute_overlap(df.formula.icc)
df.formula.icc =df.formula.icc %>% ungroup()
save(df.formula.icc, file = file.path(outreliability.comp, "icc.formula.global.rda"))
```

## icc - formula - agegroupcomarisons
```{r globalvars}
modelname = "model1_Young"
df.model1 = 
  df.parameters %>% 
   dplyr::select(feature, 
                modality, 
                mean_70y, 
                sd1, 
                ch5, 
                sdDelta_Y, 
                pct.err.mean_all)

 df.model1 = rename_model(df.model1)
 write.csv(df.model1,
            file = file.path(outreliability.comp, 
                             paste(modelname, 
                                   "csv",
                                   sep = ".")))
 
modelname="model2_Young"
df.model2 = 
  df.parameters %>% 
  dplyr::select(feature, 
                modality, 
                mean_70y, 
                sd1, 
                ch5,
                madDelta_Y, 
                pct.err.median_all)

df.model2 = rename_model(df.model2)
 write.csv(df.model2,
            file = file.path(outreliability.comp, 
                             paste(modelname, 
                                   "csv",
                                   sep = ".")))
 
modelname = "model1_Old"
df.model1 = 
  df.parameters %>% 
   dplyr::select(feature, 
                modality, 
                mean_70y, 
                sd1, 
                ch5, 
                sdDelta_O, 
                pct.err.mean_all)

 df.model1 = rename_model(df.model1)
 write.csv(df.model1,
            file = file.path(outreliability.comp, 
                             paste(modelname, 
                                   "csv",
                                   sep = ".")))
 
modelname="model2_Old"
df.model2 = 
  df.parameters %>% 
  dplyr::select(feature, 
                modality, 
                mean_70y, 
                sd1, 
                ch5,
                madDelta_O, 
                pct.err.median_all)

df.model2 = rename_model(df.model2)
 write.csv(df.model2,
            file = file.path(outreliability.comp, 
                             paste(modelname, 
                                   "csv",
                                   sep = "."))) 

model1 = import(file.path(outreliability.comp, "model1_Young.csv")) %>% 
  mutate(model = "model1_Young")
model2 = import(file.path(outreliability.comp, "model2_Young.csv")) %>% 
  mutate(model = "model2_Young")
model3 = import(file.path(outreliability.comp, "model1_Old.csv")) %>% 
  mutate(model = "model1_Old")
model4 = import(file.path(outreliability.comp, "model2_Old.csv")) %>% 
  mutate(model = "model2_Old")

model = reduce(list(model1, model2, model3, model4), rbind)

model = 
  model %>%
  rowwise() %>% 
  mutate(f = gsub(paste0("_",modality), "", feature))

df.formula.icc = expand.grid(feature = unique(model$feature),
            model = unique(model$model), 
            t = seq(3,9,by = 2), 
            total_time = seq(2,12, by =2)) %>% 
  left_join(model, .) %>% 
  mutate(ws = meanE^2*((total_time^2*t*(t+1))/ (12*(t-1)))^-1, 
         bs = seD^2, 
         icc = bs /(ws + bs))
save(df.formula.icc, file = file.path(outreliability.comp, "icc.formula.agegroup.rda"))


df.formula.icc = 
  df.formula.icc %>%
  mutate(sd_error = sqrt(ws), 
         mean1 = meanD + seD, 
         mean2 = meanD - seD)

df.formula.icc = compute_overlap(df.formula.icc)
df.formula.icc =df.formula.icc %>% ungroup()
save(df.formula.icc, file = file.path(outreliability.comp, "icc.formula.agegroup.rda"))
```
## icc - reliability between datasets
```{r}
# script for computing reliability across different datasets 
string.meas = "pct.err.mean_"
dat.me = wrapper_select_parameter_reliability(df.parameters, string.meas)
string.meas = "sdDelta_"
dat.slopeV = wrapper_select_parameter_reliability(df.parameters, string.meas)

#dat.pairwise.icc.slope = pairwise.icc.parameters(dat.slopeV)
#dat.pairwise.icc.me = pairwise.icc.parameters(dat.me)
df.formula.icc = icc_reliability_full(dat.me, dat.slopeV)
df.icc.reliability.pairwise = pairwise.reliability.icc(df.formula.icc)
df.icc.reliability.icc2 = icc2.reliability.icc(df.formula.icc)
#dat.one2all.icc.slope = one2all.icc.parameters(dat.slopeV)
#dat.one2all.icc.me = one2all.icc.parameters(dat.me)
#dat.one2all.icc.reliability = one2all.icc.reliability(df.formula.icc)

save(dat.me, 
     dat.slopeV, 
     #dat.pairwise.icc.me, 
     #dat.pairwise.icc.slope, 
     df.formula.icc, 
     df.icc.reliability.pairwise, 
     df.icc.reliability.icc2,
     #dat.one2all.icc.me,
     #dat.one2all.icc.reliability,
     file = file.path(outreliability.comp, "icc_reliability_between_samples.Rda"))

```

## power analysis - sample size calculator
```{r}
load(file.path(outreliability.comp, "icc.formula.rda"))

df.statstest  =
tribble(
  ~StatTest, ~effectsize,
  "two_sample",   .2,
  "two_sample",   .5,
  "two_sample",   .8,
  "rpearson",     .1,
  "rpearson",     .3,
  "rpearson",     .5,
  "anova3l",      .1,
  "anova3l",      .25,
  "anova3l",      .4, 
)

power = data.frame(power = .8)
df.statstest = crossing(df.statstest, power)


df.formula.icc =  sample_size_wrapper(df.formula.icc, df.statstest)

save(df.formula.icc, file = file.path(outreliability.comp, "icc.formula.rda"))
```

##individual trajectories and brain maintenance 
```{r}
model = model1
wrapper_individual_trajectories()
```

# simulation
## model1 - singler rois
```{r prepare model1}
# model 1 - sammple + s2c error
wrapper_submit_model(model1, "model1", 1000, 100, outreliability.comp, analysis) 

df.comp.model1 = summary_computational_model("model1", "single_rois", outreliability.comp)
#gs = plot_computational(outreliability.comp, modelname)
```


##model2 - single rois
```{r}
# model 2 - sele + hedges
wrapper_submit_model(model2, "model2", 1000, 100, outreliability.comp, analysis) 

df.comp.model2 = summary_computational_model("model2", "single_rois", outreliability.comp)
#gs = plot_computational(outreliability.comp, modelname)
```

# empirical
## empirical - std.error
```{r compute empirical}
load(file.path(outdir, "df.merged.Rda"))

outliers = df$outliers$delta$idx[df$outliers$delta$rmsubs.miss.data,]
delta = df$df$delta$df[df$outliers$delta$rmsubs.miss.data,]
se = df$df$delta$se[df$outliers$delta$rmsubs.miss.data,]  
se[!outliers] = NaN
db = df$df$base$df[df$outliers$delta$rmsubs.miss.data,] %>% 
  mutate(total_time = time, 
         tps = n)


# remove outliers
se = prepare_se_data(se,db) 

df.se = 
  cbind(
    db %>% filter(n >2, time > 2),
    se)

# start routine
phenos.se = names(se)[!grepl("IntraCran", names(se))]
df.emp = glmer_empirical(df.se, phenos.se, outreliability, df.harmonize)
```


## empirical to icc
```{r}
load(file.path(outdir, "df.merged.Rda"))
load(file.path(outreliability, "df.empirical.Rda"))

#load(file.path(outreliability, "df.empirical.slope.Rda"))
dat.model1 = get_simulated_results(outreliability.comp , "model1")
#dat.model2 = get_simulated_results(outreliability.comp , "model2")
#dat.simulation = rbind(dat.model1, dat.model2)
dat.simulation = dat.model1
dat.simulation = 
  dat.simulation %>% 
  mutate(t = as.numeric(as.character(tps)), 
         ws =  meanE^2*((total_time^2*t*(t+1))/ (12*(t-1)))^-1,
         beta_rmse = 100*beta_rmse/meanF, 
         avg_beta_se = 100*avg_beta_se/meanF,
         seD.obs = 100*seD.obs/meanF, 
         seD.real = 100*seD.real/meanF, 
         seD.obs2 = seD.obs ^2, 
         seD.real2 = seD.real ^2)


# relationship bettwen observed and real within subject variance
mod = lm(beta_rmse ~ avg_beta_se + avg_beta_se:log(t), data = dat.simulation)
summary(mod)

# relationship between variance and observed variance in slope (due to error propagaaaaaation)
#mod1 = lm(seD.real2 ~ seD.obs2*ws, data = dat.simulation)
#summary(mod1)

 # sd.delta = apply(delta[db$n >2 & db$time > 2,], 2, sd, na.rm = T)
 # xx = data.frame(
 #   feature = names(delta), 
 #   seD = sd.delta)

 xx = data.frame(feature = model1$feature, 
                 seD = model1$seD)
x = 
df.emp$df.out.grid.glmer %>% 
drop_na() %>% 
  filter(!feature %in% rm_vars_error)

df.emp.out = left_join(x,xx) %>% 
  rename("t" = "tps", 
         "avg_beta_se" = "fit")
df.emp.out$beta_rmse = predict(mod, df.emp.out)
df.emp.out$ws = df.emp.out$beta_rmse^2


df.emp.out = 
  df.emp.out %>%
  rowwise() %>% 
  mutate(f = gsub(paste0("_",modality), "", feature))


df.emp.out = 
  df.emp.out %>% 
 mutate(bs = seD^2, 
         icc = bs /(ws + bs))

save(df.emp.out, file = file.path(outreliability, "df.empirical_summary.Rda"))
```

```{r}
load(file = file.path(outreliability, "df.empirical_summary.Rda"))

df.statstest  =
tribble(
  ~StatTest, ~effectsize,
  "two_sample",   .2,
  "two_sample",   .5,
  "two_sample",   .8,
  "rpearson",     .1,
  "rpearson",     .3,
  "rpearson",     .5,
  "anova3l",      .1,
  "anova3l",      .25,
  "anova3l",      .4, 
)

power = data.frame(power = .8)
df.statstest = crossing(df.statstest, power)

df.emp.out = 
  df.emp.out %>% mutate(model = "empirical")
df.emp.out=  sample_size_wrapper(df.emp.out, df.statstest)

save(df.emp.out, file = file.path(outreliability, "df.empirical_summary.Rda"))
```

# Plots and figures

## Fig. scheme
```{r Fig. scheme}
gs = wrapper_figure_scheme()
```
## Fig main reliability
```{r}
outreliability.comp="/ess/p274/cluster/projects/p039_image_brain_change/data_reliability_long/df_mri/all/computational"
load(file.path(outreliability.comp, "icc.formula.rda"))
load( file.path(outreliability, "df.empirical_summary.Rda"))
# Figure main model 

oname = "model1"
df.fig = 
  df.formula.icc %>% 
  filter(model == oname)

gs1 = fig_mean_icc(df.fig, oname)
gs1.1 = fig_mean_icc_modality(df.fig, oname)

# Figurereplication model
oname = "model2"
df.fig = 
  df.formula.icc %>% 
  filter(model == oname)

gs2 = fig_mean_icc(df.fig, oname)
gs2.1 = fig_mean_icc_modality(df.fig, oname)

gs3 = fig_mean_icc(df.emp.out,"empirical")
gs2.1 = fig_mean_icc_modality(df.emp.out, "empirical")
```

## Fig. regional variability
```{r}
load(file.path(outreliability.comp, "icc.formula.rda"))
load( file.path(outreliability, "df.empirical_summary.Rda"))
fu=4
t=3

# model1
mdl = "model1"
oname = paste(mdl,"fu" ,fu,"n", t,sep =".")

df.ggseg = 
  df.formula.icc %>% 
  filter(model == mdl, 
         total_time == fu, 
         t == 3) %>% 
  rename("label" = "f")

fig_icc_regional(df.ggseg, oname)

# model2
mdl = "model2"
oname = paste(mdl,"fu" ,fu,"n", t,sep =".")

df.ggseg = 
  df.formula.icc %>% 
  filter(model == mdl, 
         total_time == fu, 
         t == 3) %>% 
  rename("label" = "f")
fig_icc_regional(df.ggseg, oname)


# empirical
mdl = "empirical"
oname = paste(mdl,"fu" ,fu,"n", t,sep =".")

df.ggseg = 
  df.emp.out%>% 
  filter(total_time == fu, 
         t == 3) %>% 
  rename("label" = "f")
fig_icc_regional(df.ggseg, oname)
```

## Fig. diff in icc across models
```{r}
load(file.path(outreliability.comp, "icc.formula.rda"))
tps = c(3,7)
time = c(2,6)
oname = "model2"
df.diff = df.formula.icc %>% 
  dplyr::select(feature, modality, icc, f,t, total_time, model) %>% 
  pivot_wider(names_from = model, values_from = icc) %>% 
  drop_na() %>% 
  mutate(diff = model1 - model2, 
                   adiff = abs(diff))

dat = 
df.diff %>% 
  group_by(feature, modality, f) %>% 
  summarise(model1 = mean(model1), 
         model2 = mean(model2), 
         diff = mean(diff), 
         adiff = mean(adiff)) %>% 
  ungroup() %>% drop_na() %>% 
  rename("label" = "f") 

fig_icc_diffs(df.diff, oname)
fig_icc_diffs_sp(df.diff, oname)
#fig_icc_diffs_sp_set_design(df.diff, oname, time, tps) 
fig_icc_regional_difference(dat, oname)
fig_mean_icc_diff(df.diff,"model2.v.1")

# empirical
oname = "empirical"

load(file.path(outreliability.comp, "icc.formula.rda"))
load( file.path(outreliability, "df.empirical_summary.Rda"))
 dat = df.formula.icc %>% 
   filter(model == "model1") %>% 
   select(feature, modality, icc, f,t, total_time, model)
dat1 = df.emp.out %>% 
  mutate(model = "empirical") %>% 
  select(feature, modality, icc, f,t, total_time, model)

df.diff = full_join(dat, dat1) 
df.diff = df.diff %>% 
  select(feature, modality, icc, f,t, total_time, model) %>% 
  pivot_wider(names_from = model, values_from = icc) %>% 
  drop_na() %>% 
  mutate(diff = model1 -empirical, 
                   adiff = abs(diff))

dat = 
df.diff %>% 
  group_by(feature, modality, f) %>% 
  summarise(model1 = mean(model1), 
         empirical = mean(empirical), 
         diff = mean(diff), 
         adiff = mean(adiff)) %>% 
  ungroup() %>% drop_na() %>% 
  rename("label" = "f") 

fig_icc_diffs(df.diff, oname)
fig_icc_diffs_sp(df.diff, oname)
#fig_icc_diffs_sp_set_design(df.diff, oname, 4, 3) 
fig_icc_regional_difference(dat, oname)
fig_mean_icc_diff(df.diff,"modele.v.1")


## between datasets
load(file.path(outreliability.comp, "icc_reliability_between_samples.Rda"))
figure_icc_across_datasets(df.icc.reliability.icc2, df.icc.reliability.pairwise)

```

## Fig. model_parameter comparison
```{r}
load(file.path(outreliability.comp, "icc_reliability_between_samples.Rda"))
gs = figure_icc_parameters(dat.me, dat.slopeV)
gs = figure_icc_parameters_bymodality(dat.me, dat.slopeV)

gs = fig_pairwise.icc.parameters(dat.slopeV, "slope")
gs = fig_pairwise.icc.parameters(dat.me, "me")
```

## Fig. equivalence between formula, simulation and empirical models
Fig. Relationship between avg_beta_se and rmse_beta
Fig. Relationship between icc from simulation and from formula
```{r}
load( file.path(outreliability.comp, "icc.formula.rda"))
dat.model1 = get_simulated_results(outreliability.comp , "model1")
#dat.model2 = get_simulated_results(outreliability.comp , "model2")
#dat = rbind(dat.model1, dat.model2)
dat = dat.model1
dat = 
dat %>% 
  mutate(t = as.numeric(as.character(tps)), 
         ws =  meanE^2*((total_time^2*t*(t+1))/ (12*(t-1)))^-1,
         beta_rmse = 100*beta_rmse/meanF, 
         avg_beta_se = 100*avg_beta_se/meanF)

gs = fig_corresponce_ws(dat)
gs = fig_compare_icc_form_sim(df.formula.icc, dat)
```

## Fig individual overlap of observations
```{r}
load(file.path(outreliability.comp, "icc.formula.rda"))
tps = c(3,7)
ttime = c(2,6, 10)
phenos =unique(df.formula.icc$feature)


fig_bc_overlap()

for (pheno in phenos) {
dat = 
  df.formula.icc %>% 
    filter(feature == pheno, 
          t %in% tps, 
          total_time %in% ttime) 
  fig_individual_overlap(dat, pheno)
}

```

## Fig. Maintenance
```{r}
phenotypes.m = 
  c("Left-Lateral-Ventricle", 
    "Left-Hippocampus", 
    "lh_entorhinal_thickness",
    "Right-Lateral-Ventricle", 
    "Right-Hippocampus",
    "rh_entorhinal_thickness")
model1 = import(file.path(outreliability.comp, "model1.csv")) %>% 
  mutate(model = "model1")

for (ft in phenotypes.m) {
  print(ft)
  gs = fig_maintainer(model1, ft) 
}

```


## Fig global variables
```{r}
gs = fig_icc_globalvars()
gss = fig_parameters_globalvars()
```
## Fig. agegroup comparison
```{r}

load(file.path(outreliability.comp, "icc.formula.agegroup.rda"))
mdl = c("model1_Young", "model1_Old")

for (p in phenos) {
  gs = fig_agegroupcomparison(df.formula.icc, p, mdl)
}
```
## fig sample size - mean & regional
```{r}
# mean sample size
load(file.path(outreliability.comp, "icc.formula.rda"))
load( file.path(outreliability, "df.empirical_summary.Rda"))

oname = "model1"

gs = fig_sample_size_mean(df.formula.icc, oname)

oname = "model2"
gs = fig_sample_size_mean(df.formula.icc, oname)


oname = "empirical"
gs = fig_sample_size_mean(df.emp.out, oname)




# regional sample size
load(file.path(outreliability.comp, "icc.formula.rda"))
dat = df.formula.icc
model = "model1"

phenotypes.samplesize = 
  c("Left-Lateral-Ventricle", 
    "Left-Hippocampus", 
    "lh_entorhinal_thickness",
    "Right-Lateral-Ventricle", 
    "Right-Hippocampus",
    "rh_entorhinal_thickness")

for (ft in phenotypes.samplesize) {
  print(ft)
  gs = fig_sample_size_region_tps(df.formula.icc, ft, model, tps = c(3,7)) 
}
```
## Fig. descriptives
```{r fig descriptives}
#longitudinal aging dataset
load(file.path(outdir, "df.all.filt.Rda"))
gs = fig_linechart(df.merge, "lifespan_full")
gs = fig_raincloud(df.merge, "lifespan_full")
db = df$df$base$df[df$outliers$delta$rmsubs.miss.data,]
gs = fig_hist_tps(db, "lifespan_full")

# empirical subset
load(file.path(outdir, "df.merged.Rda"))
db = df$df$base$df[df$outliers$delta$rmsubs.miss.data,]
db =
  db %>% 
  mutate(total_time = time, 
         tps = n) %>% 
  filter(n >2, time > 2)
dat = df.merge.long %>% 
  filter(rid %in% db$rid)
gs = fig_linechart(dat, "empirical")
gs = fig_raincloud(dat, "empirical")
gs = fig_hist_tps(db, "empirical")

# slope variance
load(file.path(outdir, "df.merged.Rda"))
db = df$df$base$df[df$outliers$delta$rmsubs.miss.data,]
db =
  db %>% 
  mutate(total_time = time, 
         tps = n) %>% 
  filter(n >3, time > 4)
dat = df.merge.long %>% 
  filter(rid %in% db$rid)
gs = fig_linechart(dat, "slope")
gs = fig_raincloud(dat, "slope")
gs = fig_hist_tps(db, "slope")

```


# Tables and stats data in mn
## Results section
### Reliability of longitudinal brain change: Simulated data.
```{r}
load(file.path(outreliability.comp, "icc.formula.rda"))
oname = "model1"
wrapper_table_aov(df.formula.icc, oname)
```

### Determinants of longitudinal reliability (II): Preprocessing stream.
```{r}
load(file.path(outreliability.comp, "icc.formula.rda"))
oname = "model2"
wrapper_table_aov(df.formula.icc, oname)
```
### Reliability of longitudinal brain change: Estimations based on empirical data.
```{r}
load( file.path(outreliability, "df.empirical_summary.Rda"))
oname = "empirical"
df.emp.out = 
  df.emp.out %>% 
  mutate(model = oname) %>% 
  ungroup()
wrapper_table_aov(df.emp.out, oname)
```

### Consistency of parameters and reliability estimates across datasets. 
```{r}
wrapper_table_parameter_comparison()


 load(file.path(outreliability.comp, "icc_reliability_between_samples.Rda"))
  
  grot = list()
  grot[[1]] = df.icc.reliability.icc2 %>%
    summarise(iccM = mean(icc),
              sd = sd(icc),
              icc.type = "ICC2") %>% 
    mutate(analysis = "global")

  grot[[2]] =
    df.icc.reliability.pairwise %>%
    summarise(iccM = mean(icc),
              sd = sd(icc),
              icc.type = "ICC(2,1)")  %>% 
    mutate(analysis = "global")


  grot[[3]] =
    df.icc.reliability.icc2 %>%
    unnest(data) %>%
    select(t, total_time, icc.sub) %>%
      summarise(iccM = mean(icc.sub), 
              sd = sd(icc.sub), 
              icc.type = "ICC2")  %>% 
    mutate(icc.type = "ICC2",
           analysis = "regional")


  grot[[4]] =
    df.icc.reliability.pairwise %>%
    unnest(data) %>%
    select(t, total_time, icc.sub) %>%
    summarise(mean(icc.sub), sd(icc.sub))  %>% 
    mutate(icc.type = "ICC(2,1)",
           analysis = "regional")
  
  icc.sumary.between.datasets.com = data.table::rbindlist(grot)
  k1 = icc.sumary.between.datasets.com  %>% 
    kable(digits = 2) %>% 
    kable_styling(full_width = FALSE) 
  fname = here("data_reliability_long/results/stats_and_tables/model_comparison", 
               paste("ICC_summary_comparison_between_datasets","html", sep = "."))
  save_kable(k1, fname)
  
  
  grot =list()
   grot[[1]] =
    df.icc.reliability.icc2 %>%
    unnest(data) %>%
    select(t, total_time, icc.sub) %>%
     group_by(t, total_time) %>% 
      summarise(iccM = mean(icc.sub), 
              sd = sd(icc.sub), 
              icc.type = "ICC2")  %>% 
    mutate(icc.type = "ICC2")


  grot[[2]] =
    df.icc.reliability.pairwise %>%
    unnest(data) %>%
    select(t, total_time, icc.sub) %>%
    group_by(t, total_time) %>% 
    summarise(mean(icc.sub), sd(icc.sub))  %>% 
    mutate(icc.type = "ICC(2,1)")
  
  icc.comparison.between.datasets.regional = data.table::rbindlist(grot) %>% 
    pivot_wider(names_from = t, 
                values_from = c(iccM, sd))
  
   k2 = icc.comparison.between.datasets.regional  %>% 
    kable(digits = 2) %>% 
    kable_styling(full_width = FALSE) 
  fname = here("data_reliability_long/results/stats_and_tables/model_comparison", 
               paste("ICC_summary_comparison_between_datasets_regional","html", sep = "."))
  save_kable(k2, fname)
```


### Consequences of longitudinal reliability (I): Sample Size Estimates.
```{r}
load(file.path(outreliability.comp, "icc.formula.rda"))
oname = "model1"
wrapper_table_effect_size(df.formula.icc, oname) 

```

###Consequences of longitudinal reliability (II): Misclassification of individual trajectories.

```{r}

  load(file.path(outreliability.comp, "icc.formula.rda"))
  oname = "model1"
   wrapper_table_individual_overlap(df.formula.icc, oname)

```

### Determinants of longitudinal reliability (I): Sample characteristics affect longitudinal reliability.
```{r}
load(file.path(outreliability.comp, "icc.formula.agegroup.rda"))
oname = "model1"
wrapper_table_agegroup(df.formula.icc, oname)
```


### Consequences of longitudinal reliability (III): Group membership based on trajectories. 
```{r}

oname = "model1"
wrapper_table_maintenance(oname)
  

```

## Methods section
### descriptives 
#### test retest dataset
```{r descriptive tables}
# Test-retest dataset
oname = "test_retest"
wrapper_table_descriptive_test_retest(oname)

```

